---
title: "template tutorial"
author: rOpenGov core team
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{template Markdown Vignette}
%\usepackage[utf8]{inputenc}
-->


Template package
===========

This R package provides a template for new packages. Your [bug reports and other
feedback](https://github.com/ropengov/template) are welcome! 


## Installation

Test the installation by loading the library:

```{r test, message=FALSE, warning=FALSE, eval=TRUE}
library(template)
```

Development version for developers:

```{r install2, eval=FALSE}
library(devtools)
install_github("ropengov/template")
```

We also recommend setting the UTF-8 encoding:

```{r locale, eval=FALSE}
Sys.setlocale(locale="UTF-8") 
```


**Validate Finnish personal identification number:**

```{r hetu2, fig.message=FALSE}
valid_hetu("010101-0101") # TRUE/FALSE
```

```{r regressionline, message=FALSE, eval=TRUE, fig.width=10, fig.height=5}
data(iris)
plot(Sepal.Length ~ Sepal.Width, iris) 
```

## Licensing and Citations

This work can be freely used, modified and distributed under the 
[Two-clause BSD license](http://en.wikipedia.org/wiki/BSD\_licenses).

```{r citation, message=FALSE, eval=TRUE}
citation("template")
```

## Session info

This vignette was created with

```{r sessioninfo, message=FALSE, warning=FALSE}
sessionInfo()
```





